---
title: "p8105_hw1_zl2977"
author: "Zhourong Li zl2977"
date: "2020/9/17"
output:
  github_document:
    df_print: paged
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggplot2)
```

## Problem 1

Create a data frame with the specified elements.

```{r create_df}

prob1_df=
   tibble(
     samp = rnorm(10),
     samp_gt_0=samp>0,
     char_vec=c("a","b","c","d","e","f","g","h","i","j"),
     factor_vec=factor(c("low","low","low","mod","mod","mod","mod","high","high","high"))
   )
```
Take the mean of each variable in my data frame.

```{r mean_pull_var}
mean(pull(prob1_df,samp))
mean(pull(prob1_df,samp_gt_0))
mean(pull(prob1_df,char_vec))
mean(pull(prob1_df,factor_vec))
```
I can take the mean of numbers and logical but not character or factor.

```{r try_numeric, results="hide"}
as.numeric(pull(prob1_df,samp_gt_0))
as.numeric(pull(prob1_df,char_vec))
as.numeric(pull(prob1_df,factor_vec))
```
```{r convert_types, results="hide"}
as.numeric(pull(prob1_df,samp_gt_0))*pull(prob1_df,samp)
as.factor(pull(prob1_df,samp_gt_0))*pull(prob1_df,samp)
as.numeric(as.factor(pull(prob1_df,samp_gt_0)))*pull(prob1_df,samp)

```



## Problem 2

```{r load_data}
data("penguins", package = "palmerpenguins")

```

The names in this data are `r names(penguins)`. The species are `r levels(penguins$species)`, the islands are `r levels(penguins$island)`, the minimum and maximum  of the bill_length_mm are {`r range(penguins$bill_length_mm,na.rm=T)`}, the minimum and maximum  of the bill_depth_mm are {`r range(penguins$bill_depth_mm,na.rm=T)`}, the minimum and maximum  of the flipper_length_mm are {`r range(penguins$flipper_length_mm,na.rm=T)`}, the minimum and maximum  of the body_mass_g are {`r range(penguins$body_mass_g,na.rm=T)`}, the sex are {`r levels(penguins$sex)`}, the start and end  of the year are {`r range(penguins$year,na.rm=T)`}. the data set has `r nrow(penguins)` rows and `r ncol(penguins)` columns, in total there are `r nrow(penguins)*ncol(penguins)` values in this data set. The mean flipper length is `r mean(penguins$flipper_length_mm,na.rm=T)`.

```{r plot_df}

plot_data<-data.frame(
  bill_length_mm=penguins$bill_length_mm,
  flipper_length_mm=penguins$flipper_length_mm
)

ggplot(plot_data,aes(x=bill_length_mm, y=flipper_length_mm))+geom_point(size=2,shape=19, color="blue")
ggsave("plot_data.png")
```